# Field surveys {#sec-field-surveys}

```{r setup}
#| include: false
#| warning: false
#| message: false
library(tidyverse)
library(DiagrammeR)
```

## GIS tools

blablabla

### Flowcharts

I would've liked to use DiagrammeR, but I cant get it to render as html.

It only renders in the interactive R session.

```{r}
#| label: flowchart
#| echo: true
#| eval: false
#| code-fold: true


create_graph() |>
  add_node(
    label="Node A"
  ) |>
  add_node(
    label = " I have a\nhyperlink"
  ) |>
  add_edge(from = 1, to = 2) |>
  select_last_nodes_created() |>
  set_node_attrs_ws(node_attr = URL, value = "https://nrk.no") |>
  add_node(
    label = "Looooooooooooooooooooong name",
    from = 1, 
    to = 2) |>
  set_node_attrs(node_attr = shape, values =  "box") |>
  select_nodes_by_id(nodes = 3) |>
  # not sure why this doesn't work:
  set_node_attrs_ws(node_attr = shape, value = "rectangle")  |>
  render_graph()
```

So we can use the integrated quarto functionality instead, mermaid or grViz (DOT).

These don't render in interactive R sessions, but show in the knitted html.

For mermaid instructions see [here](https://mermaid.js.org/syntax/flowchart.html).

```{mermaid}
flowchart LR
    A-->B
    B-->C
    B-->D
    C-->D
    click A callback "Tooltip for a callback"
    click B "https://www.github.com" "This is a tooltip for a link"
    click C call callback() "Tooltip for a callback"
    click D href "https://www.github.com" "This is a tooltip for a link"
```
